Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

@@

  plots <- plot_distribution2(mixed_data1[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 1 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data2[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 2 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data3[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 3 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

>>>>

  colors <-                 c("#e3f4f1", "#eae1f8", "#fae7fd", "#f5d0bf")
  if (size == 12) colors <- c("#a9ded7", "#d5bbf3", "#eb91f2", "#e9865b")
  if (size == 20) colors <- c("#6ec1c1", "#9d48c7", "#e44cb5", "#ce572b")
  if (size == 60) colors <- c("#357a87", "#792b9a", "#96336c", "#9a3b1a")
  if (size == 100) colors <-c("#0f2c3a", "#48185b", "#61283f", "#59230c")

@@

  plots <- plot_distribution2(mixed_data1[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 1 (n=", size, ")"), colors[2]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data2[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 2 (n=", size, ")"), colors[3]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data3[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 3 (n=", size, ")"), colors[4]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)
